\documentclass{vldb}

%========================
%  Packages
%========================

\usepackage{epsfig,endnotes}
\usepackage{graphicx,url,color}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}  %<---- for a different "look" in theorems (theorem word in bold, etc.) %ACM conflict with proof definition?
%\usepackage{subfigure}
%\usepackage[tight,footnotesize]{subfigure}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

%\usepackage{todonotes}
%\usepackage[normalem]{ulem} %strikethrough: \sout{Hello World}
%\usepackage{lastpage} %for number of pages
%\usepackage{xspace}
%\usepackage{multirow}

\usepackage[colorlinks=true,allcolors=blue,breaklinks]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{float}

%========================
%  Macros
%========================
\newcommand{\code}[1]{\textsf{\fontsize{9}{11}\selectfont #1}}

\newcommand{\inred}[1]{{\color{red}{#1}}}
\newcommand{\inpurple}[1]{{\color{blue}{#1}}}
\newcommand{\ingreen}[1]{{\color{green}{#1}}}
\newcommand{\remove}[1]{}
\newcommand{\Idit}[1]{[[\inred{Idit: #1}]]}
\newcommand{\eshcar}[1]{[[\inred{eshcar: #1}]]}
\newcommand{\anastas}[1]{[[\inpurple{Anastasia: #1}]]}
\newcommand{\tb}{\hspace{5mm}}

\newcommand{\sys}{Accordion}
\newcommand{\basic}{{\em Basic}}
\newcommand{\eager}{{\em Eager}}
\newcommand{\adp}{{\em Adaptive}}
\newcommand{\none}{{\em NoCompaction}}
\newcommand{\magic}{{\em Adaptive}}
\newcommand{\figw}{0.925\columnwidth}


\newcommand{\speedup}[1]{#1$\times$}
\newcommand{\tuple}[1]{\ensuremath{\langle \mbox{#1} \rangle}}
\newcommand{\mypara}[1]{ \vspace{8pt} \noindent{\bf #1}\hspace{6pt}}

\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

% Include information below and uncomment for camera ready
%\vldbTitle{\sys: Better Memory Organization for LSM Key-Value Stores}
%\vldbAuthors{Bortnikov, Braginsky, Hillel, Keidar, and Sheffi}
%\vldbDOI{https://doi.org/10.14778/3229863.3229873}
%\vldbVolume{11}
%\vldbNumber{12}
%\vldbYear{2018}

%========================
% Include information below and uncomment for camera ready
\vldbTitle{\sys: Better Memory Organization for LSM Key-Value Stores}
\vldbAuthors{Edward Bortnikov, Anastasia Braginsky, Eshcar Hillel, Idit Keidar, and Gali Sheffi}
\vldbDOI{https://doi.org/10.14778/3229863.3229873}

\begin{document}

\date{}

\title{\sys: Better Memory Organization\\ for LSM Key-Value Stores}

\numberofauthors{3} 
\author{
\alignauthor
Edward Bortnikov\\
       \affaddr{Yahoo Research}
       \email{ebortnik@oath.com}
\alignauthor       
Anastasia Braginsky\\
       \affaddr{Yahoo Research}
       \email{anastas@oath.com}
\alignauthor
Eshcar Hillel\\
       \affaddr{Yahoo Research}
       \email{eshcar@oath.com}
       \and
\alignauthor
Idit Keidar\\
       \affaddr{Technion and Yahoo Research}
       \email{idish@ee.technion.ac.il}       
\alignauthor
Gali Sheffi\\
       \affaddr{Yahoo Research}
       \email{gsheffi@oath.com}
} % end author

\maketitle



%=========================================================================
%  Abstract
%=========================================================================

%\subsection*{Abstract}
\abstract{
\emph{Log-structured merge (LSM)} stores have emerged as the technology of choice for building scalable 
write-intensive key-value storage systems. An LSM store replaces random I/O with sequential 
I/O by accumulating large batches of writes in a \emph{memory store} prior to flushing them to log-structured 
disk storage; the latter is continuously re-organized in the background through a \emph{compaction}
process for efficiency of reads. Though inherent to the LSM design, frequent compactions are a major pain point 
because they slow down data store operations, primarily writes, and also increase disk wear. 
Another performance bottleneck in today's state-of-the-art LSM stores, in particular ones that use
managed languages like Java,  is the 
fragmented memory layout of their dynamic memory store.

In this paper we show 
that these pain points may be mitigated via better  organization of the memory store.
We present \sys\ -- an algorithm that addresses these problems by re-applying
the LSM design principles to memory management. 
\sys\ is implemented in the production code of Apache HBase, where it 
%became the default deployment option after extensive evaluation. 
was extensively evaluated.
We demonstrate \sys's double-digit performance gains versus 
the baseline HBase implementation and discuss some unexpected lessons learned in the process. 
}
\endabstract
%========================

\section{Introduction} \label{sec:intro}
\input{intro} 

\section{Background} \label{sec:background}
\input{background} 

\section{\sys} \label{sec:accordion}
\input{accordion} 

\section{Performance Study} \label{sec:eval}

\input{eval}

\section{Related Work} \label{sec:related}
\input{related}

\section{Discussion} \label{sec:conclusions}
\input{discussion}

\subsection*{Acknowledgments}

%Need to thank some people in the HBase community.
We are thankful to the members of the HBase community for many helpful discussions during the development of the \sys\ project. In particular, we would like to thank Michael Stack, Ramakrishna Vasudevan, Anoop Sam John, Duo Zhang, Chia-Ping Tsai, and Ted Yu.

% \newpage

%\bibliographystyle{acm}
\bibliographystyle{abbrv}
\bibliography{refs}

\end{document}
