\documentclass[letterpaper,twocolumn,10pt]{article}
%\usepackage{times}
\usepackage{usenix,epsfig,endnotes}

%========================
%  Packages
%========================

\usepackage{graphicx,url,color}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}  %<---- for a different "look" in theorems (theorem word in bold, etc.) %ACM conflict with proof definition?
%\usepackage{subfigure}
%\usepackage[tight,footnotesize]{subfigure}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{times}

%\usepackage{todonotes}
%\usepackage[normalem]{ulem} %strikethrough: \sout{Hello World}
%\usepackage{lastpage} %for number of pages
%\usepackage{xspace}
%\usepackage{multirow}
%\usepackage{balance}

\usepackage[colorlinks=true,allcolors=blue,breaklinks]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{float}

%========================
%  Macros
%========================

\newcommand{\code}[1]{\textsf{\fontsize{9}{11}\selectfont #1}}

\newcommand{\inred}[1]{{\color{red}{#1}}}
\newcommand{\remove}[1]{}
\newcommand{\Idit}[1]{[[\inred{Idit: #1}]]}
\newcommand{\eshcar}[1]{[[\inred{eshcar: #1}]]}
\newcommand{\tb}{\hspace{5mm}}

\newcommand{\sys}{Accordion}
\newcommand{\basic}{{\em Basic}}
\newcommand{\eager}{{\em Eager}}
\newcommand{\adp}{{\em Adaptive}}
\newcommand{\none}{{\em None}}
\newcommand{\magic}{{\em Adaptive}}
\newcommand{\figw}{0.925\columnwidth}


\newcommand{\speedup}[1]{#1$\times$}
\newcommand{\tuple}[1]{\ensuremath{\langle \mbox{#1} \rangle}}

%========================
\begin{document}

\date{}

\title{\Large \bf  Playing HBase Tunes on \sys}


\author{
\remove{
Edward Bortnikov\footnotemark[1]  \tb
Anastasia Braginsky\footnotemark[1]  \tb
Eshcar Hillel\footnotemark[1] \tb 
Idit Keidar\footnotemark[1] \footnotemark[2] \\
	\footnotemark[1] Yahoo Research\ \ \footnotemark[2] Technion  \\ [2mm]
%\small Submission Type: Research	
}
Deployed-system paper
} % end author

\maketitle



%=========================================================================
%  Abstract
%=========================================================================

\subsection*{Abstract}

Log-sequenced-merge (LSM) trees have emerged as the technology of choice for building scalable 
write-intensive key-value storage systems. An LSM tree replaces random I/O with sequential 
I/O by accumulating large batches of writes in a \emph{memory store} prior to flushing them to log-structured 
disk storage; the latter is continuously re-organized in the background through a \emph{compaction}
process for efficiency of reads. Though inherent to the LSM design, frequent compactions are a major pain point 
because they slow down data store operations, primarily writes, and also increase disk wear.

We argue that this pain point may be mitigated via better  organization of the memory store.
%We argue that memory stores are implemented  inefficiently in the state-of-the-art 
%systems, 
We present \sys\ -- an algorithm that addresses this problem by re-applying
the battle-tested LSM tree design principles to memory management. 
\sys\ is implemented
in the production code of Apache HBase, where it became the default deployment option 
after extensive evaluation. We demonstrate \sys's double-digit performance gains versus 
the baseline HBase implementation, and discuss some unexpected lessons learned. 

\remove{
Distributed NoSQL data stores are now ubiquitously used for a wide range of Internet-scale applications, 
including search indexing, analytics, user data management, messaging, advertizing, online trading, and much much more.
Such data stores are commonly organized as  log-structured merge (LSM) trees, 
which  


This paper  reports on our experience in improving the memory organization of the popular 
Apache HBase LSM-based NoSQL store. 
We present \sys, a new memory management scheme for LSM trees, which we have implemented and 
committed in HBase 2.0.
\sys\ reduces the size of the data structure holding the 
 top LSM level, namely, the dynamic memory component that absorbs writes, and utilizes the remaining 
RAM capacity to store flat static data. This  saves space and also reduces  memory management overhead (garbage collection, etc.). 
In addition, \sys\ allows for in-memory compactions (of the flat data), whereas existing LSM-based stores compact only on-disk data. 
\sys\ thus produces  fewer disk writes, which reduces disk wear as well as disk compactions. 

Perhaps surprisingly, our experiments show that memory management overhead is a more significant bottleneck than disk I/O in a
wide range of deployments and workloads, and hence \sys\ reaps more performance benefits from flattening than from in-memory compactions,
while the latter is important for extending disk lives.
}

%========================

\section{Introduction} \label{sec:intro}
\input{intro} 


\section{Background: LSM Trees and HBase} \label{sec:background}
\input{background} 

\section{\sys} \label{sec:accordion}
\input{accordion} 

\section{\sys\ Performance} \label{sec:eval}
\input{eval}

\section{Conclusions} \label{sec:conclusions}


\subsection*{Acknowledgments}
Omitted for blind review.

\newpage

\bibliographystyle{acm}

\bibliography{refs}

\end{document}
